\begin{thebibliography}{1}

   \bibitem{baiair} Bain, W.L
   {\em Air Traffic Simulation: An Object Oriented, Discrete Event Simulation on the Intel iPSC/2 Parallel System},
	Distributed Memory Computing Conference, 1990., Proceedings of the Fifth , vol., no., pp.95-100, 8-12 Apr 1990

  \bibitem{careff} Carothers, C. D., K.S. Perumalla, and R.M. Fujimoto
   {\em Efficient optimistic parallel simulations using reverse computation},
   ACM Transactions on Modeling and Computer Simulation (TOMACS), vol. 9, 1999, p. 224–253

   \bibitem{carros} Carothers, C.D.; Bauer, D.; Pearce, S
   {\em ROSS: a high-performance, low memory, modular time warp system},
	Parallel and Distributed Simulation, 2000. PADS 2000. Proceedings. Fourteenth Workshop on , vol., no., pp.53-60, 2000     

  \bibitem{fujpar} Fujimoto, R. M. 
   {\em Parallel and Distributed Simulation Systems},
	Wiley, 2000

   \bibitem{fujane} Fujimoto, Richard, Richard Vuduc, Cong Hou, David Jefferson, Daniel Quinlan, and George Vulov
   {\em A New Method For Program Inversion},
   College of Computing, Web. 29 Mar. 2012

  \bibitem{jefvir} Jefferson, D. R.
   {\em Virtual Time},
   ACM Transactions on Programming Languages and Systems (TOPLAS), Vol. 7, 3, pp. 404-425, July 1985
  
   \bibitem{sherun} Sherry, Lance
   {\em Runway Capacity},
   George Mason University - Center for Air Transportation Systems Research, 2009
  
   \bibitem{wiepra} Wieland, F
   {\em Practical parallel simulation applied to aviation modeling},
	Parallel and Distributed Simulation, 2001. Proceedings. 15th Workship on , vol., no., pp.109-116, 2001   

   \bibitem{wiepar2} Wieland, F
   {\em Parallel simulation for aviation applications},
	Simulation Conference Proceedings, 1998. Winter , vol.2, no., pp.1191-1198 vol.2, 13-16 Dec 1998

   \bibitem{vulthe} Vulov, G.; Cong Hou; Vuduc, R.; Fujimoto, R.; Quinlan, D.; Jefferson, D
   {\em The Backstroke framework for source level reverse computation applied to parallel discrete event simulation},
	Simulation Conference (WSC), Proceedings of the 2011 Winter , vol., no., pp.2960-2974, 11-14 Dec. 2011

  \bibitem{fed1} 
   {\em Aeronautical Information Manual: Official Guide to Basic Flight Information and ATC Procedures},
	Federal Aviation Administration, February 2012  
	
  \bibitem{fed2}
   {\em Enplanements at Primary Airports (Rank Order) CY10, Air Carrier Activity Information System},
	Federal Aviation Administration, October 2011
   
  \end{thebibliography}